Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-02-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{table}
    \centering
    \caption{
        Conversion between $\lambda / D$ and mas for different wavelengths. \textbf{We should use consistent wavelengths for this table, for the Bott Plot, and for the M\&M cumulative distribution function. Also update to use the only wavelength we choose}
    }
    \label{tab:IWA_OWA}
    \begin{tabular}{ c c c c } 
    \toprule
     & $\lambda/D$ & mas (at \SI{600}{\nano\meter}) & mas (at \SI{700}{\nano\meter}) \\
    \midrule
    \midrule
    IWA & 1 & 21 & 24\\
    IWA & 2 & 42 & 48\\
    IWA & 3 & 63 & 72\\
    IWA & 4& 84& 96\\
    \midrule
    OWA & 32 & 660 & 770 \\
    OWA & 64 & 1320 & 1540\\
    \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
    \script{plot-orb-grid.py}
\end{figure*}

@@

\subsection{Circular randomly inclined orbits}
\label{sec:circular}
For each star on the \hwo target list, we generate XX hypothetical habitable planets at the Earth-equivalent-flux semi-major axis. The orbital inclinations are randomly drawn from a distribution uniform in $\cos i$. 
We then use \cref{eq:Delta_phi_max} to determine the range of accessible scattering phase angles for each hypothetical planet. 
\todo{Figure X} shows the cumulative distribution for the most extreme scattering phase angles accessible for the \hwo target list, depending on the choice of inner working angle.

@@

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/ball_of_yarn.pdf}  
    \caption{
        An example of the eccentric orbits generated for the stellar sample. %Are we putting all of these somewhere?  Its prob about 7 pages worth in total?
        The orbits are scaled by the Earth-equivalent flux distance. 
        The shaded region indicates \IWA's of 1, 2, 3 and 4\,$\lambda / D$ corresponding to 21, 42, 63 and \SI{84}{\mas}.
        The \IWA\ can significantly affect the range of scattering phases observable with each orbit.
    }
    \label{fig:ball-o-yarn}
    \script{make_yarn_plot.py} % most awesome command in this paper.  This knitter approves.
\end{figure*}

@@

\subsection{The glory of Alpha Cen}
\label{sec:ealpha-cen}
\textbf{Glory science, what it tells us (Kim)}
% Kim will write para on science of glory (what tells us, vaguely why appears here)

@@

\section{Discussion}
What did we determine? Can we actually detect this stuff for anything in this sample? Do we need to not something about things like A stars which are not included in the sample - they were rejected by the list creators - do we need to comment on this?

\section*{Software Data Availability}
%Maybe we could upload the code that we used for our analysis / plots somewhere?
%Just for full transparency / reproducibility?
The NASA ExEP target list containing the data used for these simulations is available online.% 
\footnote{\url{https://exoplanets.nasa.gov/exep/science-overview/}}
This work has made use of \textsf{numpy}
 \citep{NumPy2020}, \textsf{scipy} \citep{scipy_2020}, \textsf{matplotlib} \citep{matplotlib2007}, and \textsf{astropy},\footnote{\url{https://www.astropy.org}} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.

>>>>

\begin{table}
    \centering
    \caption{
        Conversion between $\lambda / D$ and \si{\mas} for different wavelengths, assuming $D = \SI{6}{\meter}$. 
        \todo{We should use consistent wavelengths for this table, for the Bott Plot, and for the M\&M cumulative distribution function. Also update to use the only wavelength we choose.}
    }
    \label{tab:IWA_OWA}
    \begin{tabular}{ c c c c } 
    \toprule
     & $\lambda/D$ & mas (at \SI{600}{\nano\meter}) & mas (at \SI{700}{\nano\meter}) \\
    \midrule
    \midrule
    IWA & 1 & 20.63 & 24.06 \\
    IWA & 2 & 41.25 & 48.13 \\
    IWA & 3 & 61.88 & 72.19 \\
    IWA & 4 & 82.51 & 96.26 \\
    \midrule
    OWA & 32 &  660.05 & 770.06 \\
    OWA & 64 & 1320.09 & 1540.11 \\
    \bottomrule
    \end{tabular}
\end{table}

@@

\begin{figure*}%[t]
   \centering
   \includegraphics[width=0.99\textwidth]{figures/orb-grid.pdf}
   \caption{
        \textbf{I think show your work may have borked this? The vertical arrow and the one at the top look like they got squished?} The scattering phase angles accessible to a direct imaging mission can be limited by orbital inclination or by the coronagraphic inner working angle. 
        If the orbital inclination is close to face-on (top panels) then the scattering phase angles probed throughout an orbit are limited by inclination; for circular orbits accessible scattering phases are $\phi \in 90^\circ \pm i$. 
        For orbital inclinations close to edge-on (bottom panels) the planet goes through all phases, but the scattering phase angles near 0$^\circ$ and 180$^\circ$ are not accessible due to obscuration by the coronagraph mask; for circular orbits, the accessible scattering phases are $\phi \in 90^\circ \pm \arcsin({\rm IWA}\cdot d_*/a)$.
    }
    \label{fig:orb-grid}
    \script{plot-orb-grid.py}
\end{figure*}

@@

\subsection{Circular randomly inclined orbits}
\label{sec:circular}
For each star on the \hwo\ target list, we generate XX hypothetical habitable planets at the Earth-equivalent-flux semi-major axis. The orbital inclinations are randomly drawn from a distribution uniform in $\cos i$. 
We then use \cref{eq:Delta_phi_max} to determine the range of accessible scattering phase angles for each hypothetical planet. 
\todo{Figure X} shows the cumulative distribution for the most extreme scattering phase angles accessible for the \hwo target list, depending on the choice of inner working angle.

@@

\begin{figure*}
    \centering
    \includegraphics{figures/ball_of_yarn.pdf}  
    \caption{
        %Are we putting all of these somewhere?  Its prob about 7 pages worth in total?
        Random examples of the eccentric orbits generated for the stellar sample.
        The orbits are scaled by the Earth-equivalent flux distance. 
        The concentric circles marked by the dashed lines indicate inner working angles of 1, 2, 3, and 4\,$\lambda / D$, corresponding to 20.6, 41.3, 61.9, and \SI{82.5}{\mas}, respectively (assuming $\lambda = \SI{600}{\nano\meter}$ and $D = \SI{6}{\meter}$).
        The figure illustrates that the \IWA\ can significantly affect the range of scattering phases observable with each orbit.
    }
    \label{fig:ball-o-yarn}
    \script{make_yarn_plot.py} % most awesome command in this paper.  This knitter approves.
\end{figure*}

@@

\subsection{The glory of Alpha Cen}%Halelujah
\label{sec:ealpha-cen}
\textbf{Glory science, what it tells us (Kim)}
% Kim will write para on science of glory (what tells us, vaguely why appears here)

@@

\section{Discussion}
What did we determine? Can we actually detect this stuff for anything in this sample? Do we need to not something about things like A stars which are not included in the sample - they were rejected by the list creators - do we need to comment on this?  - we decided nope.

\section*{Software/Data Availability}

The NASA ExEP target list containing the data used for these simulations is available online.% 
\footnote{\url{https://exoplanets.nasa.gov/exep/science-overview/}}
This work has made use of \textsf{numpy}
 \citep{NumPy2020}, \textsf{scipy} \citep{scipy_2020}, \textsf{matplotlib} \citep{matplotlib2007}, and \textsf{astropy},\footnote{\url{https://www.astropy.org}} a community-developed core Python package and an ecosystem of tools and resources for astronomy \citep{astropy:2013, astropy:2018, astropy:2022}.
